---
title: "Final Project"
author: "Alexander di Mauro, Kenneth Cox"
date: "4/17/2022"
output: html_document
---
Creating the initial data set & Data Cleaning
```{r}
CD = read.csv()
library(dplyr)

rt_titles = CD%>%
  rename(region = Region.of.residence, 
         age = Age.of.Subject, 
         classTime = Time.spent.on.Online.Class, 
         classRatingChr = Rating.of.Online.Class.experience, 
         classMedium = Medium.for.online.class, 
         studyTime = Time.spent.on.self.study,
         fitnessTime = Time.spent.on.fitness,
         sleepTime = Time.spent.on.sleep,
         mediaTime = Time.spent.on.social.media,
         tvTime =Time.spent.on.TV,
         preferredSocial = Prefered.social.media.platform,
         meals = Number.of.meals.per.day,
         weightChange = Change.in.your.weight,
         healthIssue = Health.issue.during.lockdown, 
         destress = Stress.busters,
         moreConnected =
         Do.you.find.yourself.more.connected.with.your.family..close.friends...relatives...,
         missMost = What.you.miss.the.most)

rateLevs = c("Very poor", "Poor", "Average", "Good", "Excellent")
CD2 = data.frame(rt_titles, classRating=factor(rt_titles$classRatingChr, levels = rateLevs))
CDFinal = CD2%>%
  select(-c(1,5,8,15,17))%>%
  mutate(tvTime = as.numeric(tvTime))
```
2.2
No code necessary

2.3
---
title: "FINAL PROJECT CODE"
author: "Jacob Wells"
date: "4/17/2022"
output: html_document
---

```{r}
library(dplyr)
library(ggplot2)
library(rvest)
```

#2.3 B
```{r}
CDFinal2=CDFinal%>%
  filter(region=="Outside Delhi-NCR", age<=25 & age>=15)%>%
  group_by(age)%>%
  summarize(avg.StudyTime=mean(studyTime,na.rm=TRUE))
```

```{r}
CDFinal3=CDFinal%>%
  filter(age>=15, age <=25)%>%
  select(region,age,studyTime)
CDFinal3%>%
  group_by(region,age)%>%
  summarize(avg.StudyTime=mean(studyTime,na.rm=TRUE))%>%
  arrange(age)
```

#2.3 C
Two-way table
```{r}
CDFinal%>%
  select(classRating,moreConnected)%>%
  table()
```
Frequency table
```{r}
table(CDFinal$region,CDFinal$preferredSocial)
```
Measure of Spread
```{r}
var(CDFinal$mediaTime)
sd(CDFinal$mediaTime)
IQR(CDFinal$mediaTime)
min(CDFinal$mediaTime)
max(CDFinal$mediaTime)
range(CDFinal$mediaTime)
```
Measure of Center
```{r}
mean(CDFinal$sleepTime)
median(CDFinal$sleepTime)
```

Table of Numerical Variables

```{r}
CDFinal3=CDFinal%>%
  filter(age>=15,age<=21)%>%
  select(region,age,tvTime)
CDFinal3%>%
  group_by(age)%>%
  summarize(avg.tvTime=mean(tvTime,na.rm=TRUE))%>%
  arrange(age)
```

2.4
(a)
```{r}
library(dplyr)
library(ggplot2)
library(RColorBrewer)
```

```{r}
Weight_data=CDFinal%>%
  group_by(weightChange)%>%
  summarise(Number=n())%>%
  mutate(Percentage=round((Number*100)/nrow(CDFinal),1))
```

```{r}

ggplot(Weight_data,aes(x=reorder(weightChange,Percentage),y=Percentage))+geom_bar(stat="identity",fill=brewer.pal(3,"Set1"))+geom_text(aes(label=Percentage))+labs(x="Weight Change",y="Percentage",title="Student Weights")+theme(plot.title=element_text(hjust=0.5))
```

```{r}

ggplot(CDFinal,aes(x=meals))+geom_histogram(bins=10,fill="turquoise",color="black")+labs(x="Meals per Day",y="Students")
```

(b)
#Data Visualization: Boxplot
```{r}
ggplot(CDFinal,aes(x=classRating, y=sleepTime,fill=weightChange))+geom_boxplot(fill="pink", color="purple", outlier.color="red")
```

#Data visualization: Scatter Plot
```{r}
ggplot(CDFinal,aes(x=studyTime,y=tvTime))+geom_point()
```

(c)
```{r}
library(ggplot2)
library(RColorBrewer)
```

Bubble Plot
```{r}
ggplot(CDFinal,aes(x=age,y=classTime,color=classRating,size=sleepTime,))+geom_point(position="jitter",alpha=0.4)+theme_classic()+labs(x="Age (Years)",y="Class Time per Day (Hours)",title = "Age vs. Daily Class Time")+theme(plot.title = element_text(hjust = 0.5))
cor(CDFinal$age,CDFinal$classTime)

ggplot(CDFinal,aes(x=classRating,fill=classMedium))+geom_bar(position = "dodge")+labs(x="Class Rating",y="Number of Observations",title = "Class Rating by Region")+theme(axis.text.x = element_text(angle = 90),plot.title = element_text(hjust = 0.5))+facet_wrap(~region)

ggplot(CDFinal,aes(x=classRating,fill=classMedium))+geom_bar(position = "fill")+labs(x="Class Rating",y="Percent of Observations",title = "Class Rating by Region")+theme(axis.text.x = element_text(angle = 90),plot.title = element_text(hjust = 0.5))+facet_wrap(~region)
```

(d)
```{r}
#source("~/statWR/cv_clean.R")
# (ignore ^)

# Word Cloud:
library(ggplot2)
library(ggwordcloud)
library(RColorBrewer)

stress<-CDFinal%>%
  group_by(destress)%>%
  summarize(count=n())%>%
  arrange(desc(count))%>%
  head(15)

ggplot(stress,aes(label=destress, size = count, color=destress))+
  geom_text_wordcloud_area()+
  theme_minimal()

# Heat Map:

sleepMap<-CDFinal%>%
  select(classMedium,classRating,sleepTime,moreConnected)%>%
  na.omit()

ggplot(sleepMap, aes(x=moreConnected, y=classRating, fill=sleepTime))+
  geom_tile(color = "white")+
  theme(axis.text.x=element_text(angle=90))+
  labs(x="More Connected?",y="Class Rating", 
         title="Sleep by Class Rating and Connection")+
  scale_fill_distiller(palette = "Greens", direction = 0)

eRating<-sleepMap%>%
  filter((classRating=="Excellent")&(moreConnected=="NO"))
# ^ investigating an apparent outlier (low sleep time associated w/ excellent rating & "no" to more connected)

summary(eRating$sleepTime) # actually pretty normal median sleep time (8hrs);
# just few observations (16) and a low minimum (5hrs)

```


2.5
```{r}
library(ggplot2)
library(caret)
library(dplyr)
```

Building the correlation matrix
```{r}
CDCor = CDFinal%>%
  select(age,classTime,studyTime,sleepTime,mediaTime,tvTime,meals)
round(cor(CDCor),2)

library(ggcorrplot)
ggcorrplot(round(cor(CDCor),2),type = "lower",lab = TRUE)
```

Building a multiple regression model
```{r}
Age_Model = train(age~classTime+studyTime+sleepTime+mediaTime,CDFinal,method = "lmStepAIC",direction = "both",trace = FALSE)
summary(Age_Model)
```
Age = 25.53 - 0.51(classTime) - 0.53(sleepTime) + 0.19(mediaTime)

Predictions (real data, interpolation, prediction)
```{r}
multi_prediction = data.frame(classTime=c(2,3.5,11),sleepTime=c(7,4.5,1),mediaTime=c(3,6.3,4),studyTime=c(4,0,0))
# The first prediction is observation 1 on the data
predict(Age_Model,multi_prediction)
```

Logistic Growth Model
```{r}
CDFinalNA = na.omit(CDFinal) # The model would spit out an error because some values were missing
Region_Model = train(region~age+classTime+studyTime+sleepTime+mediaTime+tvTime+meals,CDFinalNA,method="glmStepAIC",family="binomial",trace=FALSE)
summary(Region_Model)
Region_Model$finalModel
```
```{r}
exp(coef(Region_Model$finalModel))
```

Predictions (real data, interpolation, and extrapolation)
```{r}
log_predictions = data.frame(age=c(21,22,60),classTime=c(2,5.5,3.0),studyTime=c(4,3,2.5),sleepTime=c(7,6,7.5),mediaTime=c(3,3.4,4.1),
                             tvTime=c(1,0.5,1),meals=c(4,2,3))
# The first prediction is observation 1 on the data
predict(Region_Model,log_predictions)
```

2.6
```{r}
###

library(caret)

# plan:
# group into class ranking (see which factors might be relevant to class
# satisfaction)

# first model: classMedium, classTime
studyAndClass<-CDFinal%>%
  select(classTime,studyTime,classRating)%>%
  na.omit() 
# need to omit NA's (but leave till the end, so not omitting usable data)

ggplot(studyAndClass, aes(x=classTime,y=studyTime,color=classRating))+
  geom_point(position="jitter")

mod1<-train(classRating~classTime+studyTime, studyAndClass, method="knn")
# don't use: destress (it was categorical and allowed write-ins, so there were 
# a lot of individual unique responses which wouldn't be helpful as predictors)

mod1

timeManagement<-CDFinal%>%
  select(studyTime,sleepTime,mediaTime,tvTime,classRating)%>%
  na.omit()

modTime<-train(classRating~studyTime+sleepTime+mediaTime+tvTime, timeManagement, method="knn")


classAndMed<-CDFinal%>%
  select(classTime,classMedium,classRating)%>%
  na.omit()

modClass<-train(classRating~classTime+classMedium, classAndMed, method="knn")


homeLife<-CDFinal%>%
  select(age,meals,moreConnected,missMost,classRating)%>%
  na.omit()

modHome<-train(classRating~age+meals+moreConnected+missMost, 
            homeLife, method="knn")

comboSet<-CDFinal%>%
  select(classTime,classMedium,age,meals,moreConnected,missMost,classRating)%>%
  na.omit()

modCombo<-train(classRating~classTime+classMedium+age+meals+moreConnected+missMost, 
                comboSet, method="knn")


s1<-data.frame(classTime=mean(CDFinal$classTime),
               classMedium="Laptop/Desktop",
               age=mean(CDFinal$age),
               meals=mean(CDFinal$meals),
               moreConnected="YES",
               missMost="School/college")

predict(modClass,s1)
predict(modHome,s1)
predict(modCombo,s1)

s2<-data.frame(classTime=mean(CDFinal$classTime),
               classMedium="Laptop/Desktop",
               age=mean(CDFinal$age),
               meals=mean(CDFinal$meals),
               moreConnected="NO",
               missMost="Friends , relatives")

predict(modClass,s2)
predict(modHome,s2)
predict(modCombo,s2)

quantile(CDFinal$classTime, probs = 0.25)

s3<-data.frame(classTime=2,
               classMedium="Laptop/Desktop",
               age=mean(CDFinal$age),
               meals=mean(CDFinal$meals),
               moreConnected="NO",
               missMost="Friends , relatives")

predict(modClass,s3)
predict(modHome,s3)
predict(modCombo,s3)

s4<-data.frame(classTime=2,
               classMedium="Laptop/Desktop",
               age=mean(CDFinal$age),
               meals=mean(CDFinal$meals),
               moreConnected="YES",
               missMost="Friends , relatives")

predict(modClass,s4)
predict(modHome,s4)
predict(modCombo,s4)
```

